Minimizing post-shock forecasting error using disparate information

### 2020-06-09 manuscript/manuscript.tex
addition of more references to introduction, error fixing in dataanalysis. R(not adjust for inflation for 2008-Sep time series), and other updates in the manuscript (see 1st page)

Things to do:
\begin{enumerate}
  \item Literature review and introduction. Need more references, need to mention synthetic interventions in the introduction or the discussion.
  \item Need to add simulations. 
\end{enumerate}

@@

\begin{enumerate}
  \item Remark for non-uniqueness of $\mathbf{W}^*$ is added in Section \ref{properties}.
  \item Generalizations are added in Section 6
  \item Data analysis is updated with results of weighted adjustment estimators
  \item Some preliminary setup of the simulation is added in Section 4.
  \item RMSE is changed to MSE.
  \item Abstract is updated
  \item Edit the end of the introduction
\end{enumerate}

@@

Improving forecasts through forecast combination has a rich history \citep{bates1969combination, mundlak1978pooling, timmermann2006forecast, granger2014forecasting}.  
%\citet{timmermann2006forecast} provided several reasons for combining forecasts.  In particular, combining forecasts may be beneficial when: 1) the information set underlying individual forecasts is often unobserved to the forecast user; 2) different individual forecasts may be very differently affected by non-stationarity and model misspecifications; 3) different individual forecasts may be motivated by different loss functions \citep[and references therein]{timmermann2006forecast}. 
The classical setting for the forecast combination problem is when there are competing forecasts for a single time series.  %In this setting, one may desire combining forecasts as a method for lowering overall forecast error. %\textbf{Integrate this paragraph into the next paragraph.}
\textbf{The following list of methods needs to fall in the forecast combination literature, not the time series pooling literature}. In this setting there are a plethora of methods for combining forecasts, e.g., (1) model averaging \citep{newbold2002forecast, timmermann2006forecast, hansen2008least}, (2) model selection \citep{lee2015model, greenaway2020multistep}, (3) time-series pooling \citep{mundlak1978pooling, zellner1991forecasting, lee2020estimation, plessen2020integrated}. Model averaging typically selects weights for models based on minimizing various loss functions whereas model selection chooses the model through minimization of those loss functions, see for example, \citet{fosten2019panel} \textbf{I do not think that this reference belongs here}. Classical forecast combination may fail when forecasting in the presence of structural shocks.

@@

In our post-shock setting we combine estimated quantities from different time series with the aim of lowering forecast error for a single time series under study. Our techniques are similar to those in time-series pooling and data integration.  The literature of time-series pooling is mainly related to pooling cross-sectional panel data \citep{mundlak1978pooling, zellner1991forecasting, fosten2019panel}. The issues about whether to assume homogeneity or heterogeneity of slope coefficients across individual units are confounded. \citet{baltagi2008forecasting} showed that homogeneity approach often outperform  heterogeneity one in mean squared forecast error; while heterogeneity approach is more general to accommodate differences among units. \textbf{How does this relevant to what we are doing?}

Data integration for forecasting is a broad area of research including ideas from many areas. \citet{lee2020estimation} constructed a Bayesian hierarchical model embracing data integration %estimate posterior parameters for Richards model 
to improve predictive precision of COVID-19 infection trajectories for different countries. A similar setup may be beneficial for post-shock prediction but may be too dependent upon model specification for the shock distribution.
%, and conditions for predictive improvement are generally hard to know. 
\citet{plessen2020integrated} employed a data-mining approach to combine COVID-19 data from different countries as input to predict global net daily infections and deaths of COVID-19 using clustering. However, there is a tremendous amount of volatility in this form of COVID-19 data, and the fit of this prediction method may be improved with modeling structure or preprocessing of the donor pool. %From a machine learning perspective, 
\citet{agarwal2020two} proposed a model-free synthetic intervention method to predict unobserved potential outcomes after different interventions given a donor pool of observed outcomes with given interventions. They also provide useful guidelines for how to estimate the effects of potential interventions by giving recommendations for choosing the metric of interest, the intervention of interest, time horizons, and the donor pool.

@@

We use similar notation as that in \cite{abadie2010synthetic} to motivate 
our weighted-adjustment estimator. Consider a $n\times 1$ weight vector 
$\mbf{W}=(w_2, \ldots, w_{n+1})$, where $w_i\in [0,1]$ for all 
$i = 2, \ldots, n+1$. Construct
\begin{align*}
 \mbf{X}_1 = \begin{pmatrix}
    \mbf{x}_{1, T_1^*} \\ \mbf{x}_{1, T_1^*+1}
  \end{pmatrix}
  \quad \text{ and }
  \quad  \hat{\mbf{X}}_1(\mbf{W})
  = w_2\begin{pmatrix}
     \mbf{x}_{2, T_2^*} \\
      \mbf{x}_{2, T_2^*+1}
   \end{pmatrix} + \cdots + w_{n+1} \begin{pmatrix}
     \mbf{x}_{n+1, T_{n+1}^*} \\
      \mbf{x}_{n+1, T_{n+1}^*+1}
   \end{pmatrix} .
\end{align*}
where $\mbf{X}_1$ and $\hat{\mbf{X}}_1(\mbf{W})$ are $2 \times p$. Define $\mc{W}=\{\mbf{W}\in [0,1]^n \colon w_2+ \cdots + w_{n+1}=1 \}$. 
Suppose there exists $\mbf{W}^*\in \mc{W}$ with 
$\mbf{W}^*=(w_2^*, \ldots, w_{n+1}^*)$ such that
\begin{align}
 \mbf{X}_1=\hat{\mbf{X}}_1(\mbf{W}^*)  \quad i.e., \quad \mbf{x}_{1, T_1^*} = \sum_{i=2}^{n+1} w_i^*\mbf{x}_{i, T_i^*} \text{ and } \mbf{x}_{1, T_1^*+1} = \sum_{i=2}^{n+1} w_i^*\mbf{x}_{i, T_i^*+1}.\label{SCM}
\end{align}
 Notice that $\mbf{W}^*$ exists as long as $\mbf{X}_1$ falls in the convex hull of 
 \begin{align*}
   \left\{ \begin{pmatrix}
     \mbf{x}_{2, T_2^*} \\
      \mbf{x}_{2, T_2^*+1}
   \end{pmatrix}, \ldots, \begin{pmatrix}
     \mbf{x}_{n+1, T_{n+1}^*} \\
      \mbf{x}_{n+1, T_{n+1}^*+1}
   \end{pmatrix} \right\}.
 \end{align*}
%It is a reasonable assumption that the pool of time series that we are considering 
%should be similar to the time series of interest. 
Our weighted-adjustment estimator will therefore perform well when the pool of 
disparate time series posses similar covariates to the time series for which 
no post-shock responses are observed. We compute $\mbf{W}^*$ as
\begin{align}
  \mbf{W}^* = \argmin_{\mbf{W}\in \mc{W}} \norm{\mrm{vec}\big(\mbf{X}_1-\hat{\mbf{X}}_1(\mbf{W})\big)}_{2p}. 
  \label{W}
\end{align}
%which is a more general form of $\mbf{W}^*$ for the case when $\mbf{X}_1$ does not fall in the convex hull of (\ref{convexhull}). 
We stress that $\mathbf{W}^*$ may not be unique. \cite{abadie2010synthetic} commented that we can select $\mbf{W}^*$ 
so that (\ref{SCM}) holds approximately %so that the property of $\mbf{W}^*$ should 
%still hold approximately 
and that weighted-adjustment estimation techniques of this form are not 
appropriate when the fit is poor. 
Note that $\mbf{W}^*$ is not random since the covariates are assumed to be fixed. Since $\mc{W}$ is a closed and bounded subset of $\reals^n$,  $\mc{W}$ is compact. Because the objective function 
is continuous in $\mbf{W}$, $\mbf{W}^*$ will always exist. %Relying on this weight, 
%we are mainly interested in constructing the following adjustment estimator:
Our weighted-adjustment estimator for the shock effect $\alpha_1$ is
  \begin{align*}
    \hat{\alpha}_{\rm wadj} = \sum_{i=2}^{n+1} w_i^*\hat{\alpha}_i
    \quad \text{ for } \quad \mbf{W}^* = \begin{pmatrix}
      w^*_2 & \cdots & w^*_{n+1}
    \end{pmatrix}.
  \end{align*}
 %Different from \citet{abadie2010synthetic}, our construction customizes synthetic control methods to the setting of AR(1) model. To be more specific, notice that (\ref{SCM}) implicitly uses the covariates at $T_*$ the shock-time and $T_*-1$ the time point just before the shock. This model somehow accounts for the impact of past information on the shock-effects. 
Estimation properties of $\hat{\alpha}_{\rm adj}$, $\hat{\alpha}_{\rm IVW}$, 
and $\hat{\alpha}_{\rm wadj}$ are discussed in the remaining sections.

@@

\begin{remark}
  In Section \ref{constructionofestimators}, we note that $\mathbf{W}^*$ may not be unique. However, Proposition \ref{proprisk} and \ref{propriskwadj2} will hold for  every $\hat{\alpha}_{\rm wadj}$ using  $\mathbf{W}^*$ that satisfies (\ref{SCM}).
\end{remark}

@@

The bootstrap based on resampling the donor pool with replacement is the same as above with the addition of first round of sampling $n$ values from $I=\{2, \ldots, n+1\}$ without replacement to generate  $I^*$. Then, it follows the same step with the one conditioned on the donor pool by replacing $I$ by $I^*$. Care is needed when using this bootstrap procedure to estimate the variability of $\hat{\alpha}_{\mrm{wadj}}$. When the rank of the design matrix corresponding to the mean function of $\alpha_i$ under $\mc{M}_2$ is greater than $n$ then our bootstrap procedure will work fine, however, if the constraints used to obtain $\mathbf{W}^*$ are binding then our bootstrap procedure needs to be modified \citep{li2019statistical}. The subsampling method in Section 4 of \citet{li2019statistical} can be adapted to our post-shock setting when the constraints are binding.

Let 
$
  \overline{\hat{\alpha}_{\mrm{adj}}} 
    = \frac{1}{B} \sum_{b=1}^B \sum_{i=2}^{n+1}\hat{\alpha}_i^{(b)}
$, 
$
  \overline{\hat{\alpha}_{\mrm{wadj}}} 
    = \frac{1}{B} \sum_{b=1}^B \sum_{i=2}^{n+1}w_i^* \hat{\alpha}_i^{(b)}
$, 
and 
$
  \overline{\hat{\alpha}_{\mrm{IVW}}} 
    = \frac{1}{B} \sum_{b=1}^B \sum_{i=2}^{n+1}\hat{\alpha}_{{\rm IVW}, i}^{(b)}.
$
The almost-sure convergence results for $\hat{\alpha}_{\mrm{adj}}$ and $\hat{\alpha}_{\mrm{wadj}}$ follow naturally, provided that the regularity conditions outlined in \citet{bose1988edgeworth} hold. The proof for the case of $\overline{\hat{\alpha}_{\mrm{wadj}}}$, the sample mean of the bootstrapped weighted adjustment estimator, can be presented as below. As $B \to \infty$,
\begin{align*}
  \overline{\hat{\alpha}_{\mrm{wadj}}}
  = \frac{1}{B} \sum_{b=1}^B \sum_{i=2}^{n+1}w_i^* \hat{\alpha}_i^{(b)}
  = \sum_{i=2}^{n+1}w_i^* \frac{1}{B} \sum_{b=1}^B\hat{\alpha}_i^{(b)}
  \overset{a.s.}{\rightarrow} \sum_{i=2}^{n+1}w_i^* \alpha_i 
  =\E{\hat{\alpha}_{\rm wadj}|\Theta},
\end{align*}
The case for the sample variance of the bootstrapped weighted adjustment estimator is similar. The same rationale holds for the adjustment estimator as well since it is a linear combination of OLS estimates, and the weights are not random conditioned on $\Theta$. However, the case for $\hat{\alpha}_{\rm IVW}$ is slightly different because it is a linear combination of OLS estimates with random weights. It is not clear with respect to whether similar consistency results holds for $\hat{\alpha}_{\rm IVW}$. We claim that our bootstrap procedure provides an approximation for the case of $\hat{\alpha}_{\rm IVW}$.

@@

In this section, we provide justification for our methods based on simulation examples. We implement our simulation based on $\mc{M}_{22}$ with negligibly small $\Sigma_{\gamma}$ and $\Sigma_{\delta}$ approximating the design of $\mathcal{M}_{21}$.  $\phi_i$'s are sampled independently from $\mrm{Uniform}(0,1)$. We  sampled $T_i$'s  independently from  $\Gamma(10, 5)$ that are further rounded to integers. It is designed to illustrate the performance of $\hat{\alpha}_{\rm IVW}$ that may perform well in time series with varying lengths. Moreover, we generated the covariates from $\Gamma(1,10)$ to set up a setting when the $\hat{\alpha}_{\rm wadj}$ may perform well. We consider $p=2$ and $\mu_{\alpha}=10$. In this experiment, we consider parameter setup by varying $\sigma$ in the model of $y_{i,t}$, $n$, the donor pool size, and $\sigma_{\gamma}$ and $\sigma_{\delta}$ in the model $\delta_i \sim \normal{2\mathbf{1}_p}{\sigma^2_{\delta}\mathbf{I}_p}$, and $\gamma_i \sim \normal{2\mathbf{1}_p}{\sigma^2_{\gamma}\mathbf{I}_p}$.

@@

Specifically, we verify the unbiasedness results in Proposition \ref{unbiased}, and consistency of our proposed risk-reduction propositions. We define the consistency by whether our risk-reduction propositions yield results that agree with the reality that can be known in the simulation. Suppose we make the decision to  accept $\hat{\alpha}$ for $\hat{\alpha}\in \{\hat{\alpha}_{\rm adj}, \hat{\alpha}_{\rm wadj}, \hat{\alpha}_{\rm IVW}\}$ if risk-reduction proposition reports that $\hat{\alpha}$ reduces the risk, and reject $\hat{\alpha}$ otherwise. Consistency can be interpreted in a similar way to hypothesis testing with the following confusion table. 
\begin{center}
  \begin{center}
      \begin{tabular}{cc|c|c}
        \hline
        & & \multicolumn{2}{c}{Decision} \\
        & & Use $\hat{\alpha}$ & Do not use $\hat{\alpha}$ \\ 
                \hline
     \multirow{2}{*}{Truth}  & $R_{T_1^*+1,2}<R_{T_1^*+1,1}$ & Consistent & Inconsistent\\
      \cline{3-4}
      & $R_{T_1^*+1,2}>R_{T_1^*+1,1}$   & Inconsistent & Consistent \\
      \hline
      \end{tabular}
  \end{center}
\end{center}
We report 1 for risk-reduction propositions to be consistent and 0 otherwise.

@@

@@

We assume that the five shocks are independent of the shock that Conoco Phillips experienced on March 9, 2020. The covariates and response of time series in the donor pool are adjusted for inflation. Note that there are three shock-effects nested in the time series 2008 September, we assume that these three shocks are independent. We computed 3 shock-effect estimates. Using the same model that is described in $\mc{M}_{2}$ (see Section \ref{modelsetup}), we computed 3 shock-effect estimates, namely the adjustment  $\hat{\alpha}_{\rm adj}$, weighted adjustment $\hat{\alpha}_{\rm wadj}$, and the inverse-variance weighted $\hat{\alpha}_{\rm IVW}$. For $\hat{\alpha}_{\rm wadj}$, the fitting result can be described by
\begin{align*}
 \mathbf{W}^*= (0.000,0.000, 0.949, 0.000, 0.051) \quad \text{ and } \quad  \norm{\mrm{vec}\big(\mbf{X}_1-\hat{\mbf{X}}_1(\mbf{W}^*)\big)}_{4} = 23.496.
\end{align*}
Note that the norm is computed using the $k$-dimensional Euclidean metric. The fit is acceptable. According to discussions in Section \ref{constructionofestimators}, the property of $\hat{\alpha}_{\rm wadj}$ should hold approximately. The solution $\mathbf{W}^*$ reports that the $\alpha_1$ is similar to $\alpha_3$ (September 8, 2008) and $\alpha_5$ (November 27, 2014) under the setup of $\mc{M}_2$ and our collected covariates.

\begin{table}[H]
  \caption{Bootstrap estimates and results yielded by risk-reduction propositions with $B = 1000$}\label{table2}
  \begin{center}
    \begin{tabular}{lrrr}
      & $\hat{\alpha}_{\rm adj}$ & $\hat{\alpha}_{\rm wadj}$ & $\hat{\alpha}_{\rm IVW}$ \\
      \hline 
    Bootstrapped mean  & $-5.340$ & $-5.014$ & $-5.287$ \\
    Bootstrapped variance & 0.508 & 0.480 & 2.821 \\
    Risk-reduction proposition & 1 & 1 & 1
%    Best shock-effect estimator & 0 & 1 & 0
    \end{tabular}
  \end{center}  
\end{table}
\vspace{-.5cm}

>>>>

Things to do:
\begin{enumerate}
  \item Need to add simulations. 
\end{enumerate}

@@

\begin{enumerate}
  \item Proposition for uniqueness of $\mathbf{W}^*$ is added.
  \item Introduction is revised with additional references.
  \item Data analysis is revised by fixing previous coding error.
  \item Simulation description is updated.
  \item Discussion is revised according to comments.
\end{enumerate}

@@

Improving forecasts through forecast combination has a rich history \citep{bates1969combination, mundlak1978pooling, timmermann2006forecast, granger2014forecasting}.  
%\citet{timmermann2006forecast} provided several reasons for combining forecasts.  In particular, combining forecasts may be beneficial when: 1) the information set underlying individual forecasts is often unobserved to the forecast user; 2) different individual forecasts may be very differently affected by non-stationarity and model misspecifications; 3) different individual forecasts may be motivated by different loss functions \citep[and references therein]{timmermann2006forecast}. 
The classical setting for the forecast combination problem is when there are competing forecasts for a single time series.  %In this setting, one may desire combining forecasts as a method for lowering overall forecast error. %\textbf{Integrate this paragraph into the next paragraph.}
In this setting there are a plethora of methods for combining forecasts, e.g., model averaging \citep{newbold2002forecast, hendry2004pooling, koop2004forecasting, timmermann2006forecast, eklund2007forecast, hansen2008least}, model selection \citep{swanson1997model, swanson2001choosing, lee2015model}, and other various methods \citep{pesaran2011forecast,li2014forecasting}. Forecast encompassing methods are developed to test whether competing forecasts are suitable for combinations \citep{newbold2002forecast, fang2003forecasting}.

@@

% In our post-shock setting we combine estimated quantities from different time series with the aim of lowering forecast error for a single time series under study. Our techniques are similar to those in time-series pooling and data integration.  The literature of time-series pooling is mainly related to pooling cross-sectional panel data \citep{mundlak1978pooling, zellner1991forecasting, fosten2019panel}. The issues about whether to assume homogeneity or heterogeneity of slope coefficients across individual units are confounded. \citet{baltagi2008forecasting} showed that homogeneity approach often outperform  heterogeneity one in mean squared forecast error; while heterogeneity approach is more general to accommodate differences among units. \textbf{How does this relevant to what we are doing?}

Data integration for forecasting is a broad area of research including ideas from many areas. Time-series pooling methods are a popular data integration method for panel data \citep{zellner1991forecasting, hoogstrate2000pooling, baltagi2008forecasting, fosten2019panel, liu2020forecasting}.  However, the issues about whether to assume homogeneity or heterogeneity of slope coefficients across individual units are confounded.  \citet{lee2020estimation} constructed a Bayesian hierarchical model embracing data integration %estimate posterior parameters for Richards model 
to improve predictive precision of COVID-19 infection trajectories for different countries. A similar setup may be beneficial for post-shock prediction but may be too dependent upon model specification for the shock distribution.
%, and conditions for predictive improvement are generally hard to know. 
\citet{plessen2020integrated} employed a data-mining approach to combine COVID-19 data from different countries as input to predict global net daily infections and deaths of COVID-19 using clustering. However, there is a tremendous amount of volatility in this form of COVID-19 data, and the fit of this prediction method may be improved with modeling structure or preprocessing of the donor pool. %From a machine learning perspective, 
\citet{agarwal2020two} proposed a model-free synthetic intervention method to predict unobserved potential outcomes after different interventions given a donor pool of observed outcomes with given interventions. They also provide useful guidelines for how to estimate the effects of potential interventions by giving recommendations for choosing the metric of interest, the intervention of interest, time horizons, and the donor pool.

@@

We use similar notation as that in \cite{abadie2010synthetic} to motivate 
our weighted-adjustment estimator. Consider a $n\times 1$ weight vector 
$\mbf{W}=(w_2, \ldots, w_{n+1})$, where $w_i\in [0,1]$ for all 
$i = 2, \ldots, n+1$. Construct
 \mbf{X}_1 = \begin{pmatrix}
    \mbf{x}_{1, T_1^*} \\ \mbf{x}_{1, T_1^*+1}
  \end{pmatrix}
  \quad \text{ and }
  \quad  \hat{\mbf{X}}_1(\mbf{W})
  = w_2\begin{pmatrix}
     \mbf{x}_{2, T_2^*} \\
      \mbf{x}_{2, T_2^*+1}
   \end{pmatrix} + \cdots + w_{n+1} \begin{pmatrix}
     \mbf{x}_{n+1, T_{n+1}^*} \\
      \mbf{x}_{n+1, T_{n+1}^*+1}
   \end{pmatrix} .
where $\mbf{X}_1$ and $\hat{\mbf{X}}_1(\mbf{W})$ are $2 \times p$. Define $\mc{W}=\{\mbf{W}\in [0,1]^n \colon w_2+ \cdots + w_{n+1}=1 \}$. 
Suppose there exists $\mbf{W}^*\in \mc{W}$ with 
$\mbf{W}^*=(w_2^*, \ldots, w_{n+1}^*)$ such that
 \mbf{X}_1=\hat{\mbf{X}}_1(\mbf{W}^*)  \quad i.e., \quad \mbf{x}_{1, T_1^*} = \sum_{i=2}^{n+1} w_i^*\mbf{x}_{i, T_i^*} \text{ and } \mbf{x}_{1, T_1^*+1} = \sum_{i=2}^{n+1} w_i^*\mbf{x}_{i, T_i^*+1}.\label{SCM}
 Notice that $\mbf{W}^*$ exists as long as $\mbf{X}_1$ falls in the convex hull of 
   \left\{ \begin{pmatrix}
     \mbf{x}_{2, T_2^*} \\
      \mbf{x}_{2, T_2^*+1}
   \end{pmatrix}, \ldots, \begin{pmatrix}
     \mbf{x}_{n+1, T_{n+1}^*} \\
      \mbf{x}_{n+1, T_{n+1}^*+1}
   \end{pmatrix} \right\}.
%It is a reasonable assumption that the pool of time series that we are considering 
%should be similar to the time series of interest. 
Our weighted-adjustment estimator will therefore perform well when the pool of 
disparate time series posses similar covariates to the time series for which 
no post-shock responses are observed. We compute $\mbf{W}^*$ as
  \mbf{W}^* = \argmin_{\mbf{W}\in \mc{W}} \norm{\mrm{vec}\big(\mbf{X}_1-\hat{\mbf{X}}_1(\mbf{W})\big)}_{2p}. 
  \label{W}
%which is a more general form of $\mbf{W}^*$ for the case when $\mbf{X}_1$ does not fall in the convex hull of (\ref{convexhull}). 
\cite{abadie2010synthetic} commented that we can select $\mbf{W}^*$ 
so that (\ref{SCM}) holds approximately %so that the property of $\mbf{W}^*$ should 
%still hold approximately 
and that weighted-adjustment estimation techniques of this form are not 
appropriate when the fit is poor. 
Note that $\mbf{W}^*$ is not random since the covariates are assumed to be fixed. Since $\mc{W}$ is a closed and bounded subset of $\reals^n$,  $\mc{W}$ is compact. Because the objective function 
is continuous in $\mbf{W}$, $\mbf{W}^*$ will always exist. %Relying on this weight, 
%we are mainly interested in constructing the following adjustment estimator:
Our weighted-adjustment estimator for the shock effect $\alpha_1$ is
    \hat{\alpha}_{\rm wadj} = \sum_{i=2}^{n+1} w_i^*\hat{\alpha}_i
    \quad \text{ for } \quad \mbf{W}^* = \begin{pmatrix}
      w^*_2 & \cdots & w^*_{n+1}
    \end{pmatrix}.
 %Different from \citet{abadie2010synthetic}, our construction customizes synthetic control methods to the setting of AR(1) model. To be more specific, notice that (\ref{SCM}) implicitly uses the covariates at $T_*$ the shock-time and $T_*-1$ the time point just before the shock. This model somehow accounts for the impact of past information on the shock-effects. 
  \mathbf{V} = \Big(\mrm{vec}\big((\mathbf{x}_{2, T_2^*}, \mathbf{x}_{2, T_2^*+1})\big), \ldots, \mrm{vec}\big((\mathbf{x}_{n+1, T_2^*}, \mathbf{x}_{n+1, T_2^*+1})\big)\Big).
Note that $\mathbf{V}$ is $2p \times n$. Then, the following proposition details some conditions when $\mathbf{W}^*$ is unique.
\begin{prop}
  \label{uniqueness} If $\mathbf{V}$ has full rank and it exists some $\mathbf{W}$ satisfies (\ref{SCM}), the solution to  (\ref{W}) is unique.
\end{prop} 
If the covariates are of full rank and the true solution lies in the convex and compact $\mathcal{W}$, a sufficient condition for $\mathbf{W}^*$ to be unique is $2p \geq n$. However, when $2p < n$, $\mathbf{W}^*$ may not be unique.

Estimation properties of $\hat{\alpha}_{\rm adj}$, $\hat{\alpha}_{\rm IVW}$, 
and $\hat{\alpha}_{\rm wadj}$ are discussed in the remaining sections.

@@

\begin{remark}
  In Section \ref{constructionofestimators}, we noted that $\mathbf{W}^*$ may not be unique if $2p < n$. However, Proposition \ref{proprisk} and \ref{propriskwadj2} will hold for  every $\hat{\alpha}_{\rm wadj}$ using  $\mathbf{W}^*$ that satisfies (\ref{SCM}).
\end{remark}

@@

The bootstrap based on resampling the donor pool with replacement is the same as above with the addition of first round of sampling $n$ values from $I=\{2, \ldots, n+1\}$ without replacement to generate  $I^{(b)}$. Then, it follows the same step with the one conditioned on the donor pool by replacing $I$ by $I^{(b)}$. Care is needed when using this bootstrap procedure to estimate the variability of $\hat{\alpha}_{\mrm{wadj}}$. When the rank of the design matrix corresponding to the mean function of $\alpha_i$ under $\mc{M}_2$ is greater than $n$ then our bootstrap procedure will work fine, however, if the constraints used to obtain $\mathbf{W}^*$ are binding then our bootstrap procedure needs to be modified \citep{li2019statistical}. The subsampling method in Section 4 of \citet{li2019statistical} can be adapted to our post-shock setting when the constraints are binding.

Let 
$
  \overline{\hat{\alpha}_{\mrm{adj}}} 
    = \frac{1}{B} \sum_{b=1}^B \sum_{i=2}^{n+1}\hat{\alpha}_i^{(b)}
$, 
$
  \overline{\hat{\alpha}_{\mrm{wadj}}} 
    = \frac{1}{B} \sum_{b=1}^B \sum_{i=2}^{n+1}w_i^* \hat{\alpha}_i^{(b)}
$, 
and 
$
  \overline{\hat{\alpha}_{\mrm{IVW}}} 
    = \frac{1}{B} \sum_{b=1}^B \sum_{i=2}^{n+1}\hat{\alpha}_{{\rm IVW}, i}^{(b)}.
$
The almost-sure convergence results for $\hat{\alpha}_{\mrm{adj}}$ and $\hat{\alpha}_{\mrm{wadj}}$ follow naturally, provided that the regularity conditions outlined in \citet{bose1988edgeworth} hold. The proof for the case of $\overline{\hat{\alpha}_{\mrm{wadj}}}$, the sample mean of the bootstrapped weighted adjustment estimator, can be presented as below. As $B \to \infty$,
\begin{align*}
  \overline{\hat{\alpha}_{\mrm{wadj}}}
  = \frac{1}{B} \sum_{b=1}^B \sum_{i=2}^{n+1}w_i^* \hat{\alpha}_i^{(b)}
  = \sum_{i=2}^{n+1}w_i^* \frac{1}{B} \sum_{b=1}^B\hat{\alpha}_i^{(b)}
  \overset{a.s.}{\rightarrow} \sum_{i=2}^{n+1}w_i^* \alpha_i 
  =\E{\hat{\alpha}_{\rm wadj}|\Theta}.
\end{align*}
The case for the sample variance of the bootstrapped weighted adjustment estimator is similar. The same rationale holds for the adjustment estimator as well since it is a linear combination of OLS estimates, and the weights are not random conditioned on $\Theta$. However, the case for $\hat{\alpha}_{\rm IVW}$ is slightly different because it is a linear combination of OLS estimates with random weights. It is not clear with respect to whether similar consistency results holds for $\hat{\alpha}_{\rm IVW}$. We claim that our bootstrap procedure provides an approximation for the case of $\hat{\alpha}_{\rm IVW}$.

@@

In this section, we provide justification for our methods based on simulation examples. We implemented our simulation based on $\mc{M}_{22}$ with negligibly small $\Sigma_{\gamma}$ and $\Sigma_{\delta}$ approximating the design of $\mathcal{M}_{21}$.  We consider $p=13$ and $\mu_{\alpha}=10$, where $p = 13$ is set to satisfy conditions in Proposition \ref{uniqueness}.

Parameter setup of our simulations are detailed as below. $\phi_i$'s are sampled independently from $\mrm{Uniform}(0,1)$. We  sampled $T_i$'s  independently from  $\Gamma(10, 5)$ that are further rounded to integers. This process is repeated until $T_i > 2p + 3$ for all $i\in \{1, \ldots, n + 1\}$ to satisfy a necessary condition for the design matrix of OLS estimation to have full rank. It is designed to illustrate the performance of $\hat{\alpha}_{\rm IVW}$ that may perform well in time series with varying lengths. Moreover, we generated the covariates from $\Gamma(1,10)$ to set up a setting when the $\hat{\alpha}_{\rm wadj}$ may perform well.

In this experiment, we consider parameter setup by varying $\sigma$ in the model of $y_{i,t}$, $n$, the donor pool size, and $\sigma_{\gamma}$ and $\sigma_{\delta}$ in the model $\delta_i \sim \normal{2\mathbf{1}_p}{\sigma^2_{\delta}\mathbf{I}_p}$, and $\gamma_i \sim \normal{2\mathbf{1}_p}{\sigma^2_{\gamma}\mathbf{I}_p}$. We used 200 replications of Monte Carlo simulations and $B = 500$ for computation; and report means and standard errors for estimated quantities accordingly.

@@

Specifically, we verify the unbiasedness results in Proposition \ref{unbiased}, and consistency of our proposed risk-reduction propositions. We define the consistency by whether our risk-reduction propositions yield results that agree with the reality that can be known in the simulation. Suppose we make the decision to  accept $\hat{\alpha}$ for $\hat{\alpha}\in \{\hat{\alpha}_{\rm adj}, \hat{\alpha}_{\rm wadj}, \hat{\alpha}_{\rm IVW}\}$ if risk-reduction proposition reports that $\hat{\alpha}$ reduces the risk, and reject $\hat{\alpha}$ otherwise. Consistency can be interpreted in a similar way to hypothesis testing with the following confusion table. 
\begin{center}
  \begin{center}
      \begin{tabular}{cc|c|c}
        \hline
        & & \multicolumn{2}{c}{Decision} \\
        & & Use $\hat{\alpha}$ & Do not use $\hat{\alpha}$ \\ 
                \hline
     \multirow{2}{*}{Truth}  & $R_{T_1^*+1,2}<R_{T_1^*+1,1}$ & Consistent & Inconsistent\\
      \cline{3-4}
      & $R_{T_1^*+1,2}>R_{T_1^*+1,1}$   & Inconsistent & Consistent \\
      \hline
      \end{tabular}
  \end{center}
\end{center}
We report 1 for risk-reduction propositions to be consistent and 0 otherwise. Recall that in Section \ref{comparisons}, we could estimate the risk-reduction quantities, and therefore select the best estimator with the maximum risk-reduction quantities. It is also possible to confirm whether this decision is true in a simulation setting. Similarly, we report 1 for the decision of selecting the best shock-effect estimators  to be consistent and 0 otherwise.

In the first experiment, we consider the parameter combination of  $n \in \{5, 10, 15, 25\}$ and $\sigma_{\gamma}= \sigma_{\delta}=\sigma_{\alpha} \in  \{0.01, 0.1, 1, 10\}$ where we fix $\sigma$ to 1. The bias results are not reported for $\hat{\alpha}_{\rm IVW}$ since its moments are generally unknown. It is shown in Table ? that as the donor pool size increases, the bias and consistency results improve with more precision. In contrast, the result gets poorer as  the variance of $\alpha_i$ increases. It is to be expected since the consistency results claimed in Section \ref{varbootstrap} are conditioned on $\Theta$. Under a fixed design, it is evident that the results of our risk-reduction propositions are highly consistent if the models for $\alpha_i$'s  are identified correctly with appropriate covariates. But it is reversed in the random design case.

@@

In the first experiment, Table ? shows similar results to  Section  \ref{parametricbootstrapsimulation} that the prediction and distance to $\alpha_1$ gets better as $n$ increases but worser when the variance of $\alpha_i$ gets larger.

@@

We assume that the five shocks are independent of the shock that Conoco Phillips experienced on March 9, 2020. The covariates and response of time series in the donor pool are adjusted for inflation. Note that there are three shock-effects nested in the time series 2008 September, we assume that these three shocks are independent, where the assumption checks using likelihood ratio test are provided in Appendix \ref{smfda}. We computed 3 shock-effect estimates. Using the same model that is described in $\mc{M}_{2}$ (see Section \ref{modelsetup}), we computed 3 shock-effect estimates, namely the adjustment  $\hat{\alpha}_{\rm adj}$, weighted adjustment $\hat{\alpha}_{\rm wadj}$, and the inverse-variance weighted $\hat{\alpha}_{\rm IVW}$. For $\hat{\alpha}_{\rm wadj}$, the fitting result can be described by
\begin{align*}
 \mathbf{W}^*= (0.000,0.000, 0.949, 0.000, 0.051) \quad \text{ and } \quad  \norm{\mrm{vec}\big(\mbf{X}_1-\hat{\mbf{X}}_1(\mbf{W}^*)\big)}_{4} = 23.496.
\end{align*}
Note that the norm is computed using the $k$-dimensional Euclidean metric. The fit is acceptable. According to discussions in Section \ref{constructionofestimators}, the property of $\hat{\alpha}_{\rm wadj}$ should hold approximately. The solution $\mathbf{W}^*$ reports that the $\alpha_1$ is similar to $\alpha_3$ (September 8, 2008) and $\alpha_5$ (November 27, 2014) under the setup of $\mc{M}_2$ and our collected covariates.

\begin{table}[H]
  \caption{Bootstrap estimates and results yielded by risk-reduction propositions with $B = 1000$}\label{table2}
  \begin{center}
    \begin{tabular}{lrrr}
      & $\hat{\alpha}_{\rm adj}$ & $\hat{\alpha}_{\rm wadj}$ & $\hat{\alpha}_{\rm IVW}$ \\
      \hline 
    Bootstrapped mean  & $-5.340$ & $-5.014$ & $-5.287$ \\
    Bootstrapped variance & 0.508 & 0.480 & 2.821 \\
    Risk-reduction proposition & 1 & 1 & 1\\
    Risk reduction & 28.126 & 28.179 & 25.834
    \end{tabular}
  \end{center}  
\end{table}
\vspace{-.5cm}

Using the parametric bootstrap proposed in Section \ref{varbootstrap}, we estimated parameters for risk-reduction propositions and risk-reduction quantities proposed in  Section \ref{properties}; and the result is presented in Table \ref{table2}. The estimated risk-reduction quantities  vote $\hat{\alpha}_{\rm wadj}$  for the best estimator. Note that this parametric bootstrap procedure is conditioned  on the  donor pool. Table \ref{table2} tells that all three proposed  shock-effect estimators are usable in the sense that the forecast employing them is better than the one without; and the $\hat{\alpha}_{\rm wadj}$ is the best in terms of the estimated risk-reduction quantity. Then, we verify the consistency of the result yielded by risk-reduction propositions with the reality as below.
